Proposed Solution

### 2017-01-25 CAV17/secs/intro.tex
stuff

@@

Our learning algorithm surmounts all of difficulties present in 
existing tools.  \app implements a learning
algorithm inspired by {\em rule association
learning}~\cite{agrawal1993mining}. It analyzes a large training set of configuration  files~\cite{configdataset}. Those are real-world reported misconfigurations. A file in the training set might 
contain several different errors and these errors only appear 
in a small percentage of files. We first translate those file into an 
intermediary typed language. With with every type we associate 
a set of very general interfaces. An \app's user does not
need to provide them, they are internally associated to the types. The 
learner then instantiates those interfaces with the keywords appearing in 
the training set. However, since files might also contain errors we take 
this into account when learning correct rules. All learned rules are 
annotated with the probability of correctness.  
To ensure the learned rules are good enough,
\app employs a further analysis to refine the learned rules.
In general, \app builds a graph modeling the learned rules,
and then analyzes this graph to rank the importance
and relevance of the learned rules.

We have implemented a tool, \app, and evaluated it on almost 1000 real-world configuration files from Github.
We demonstrate that we are able to detect known errors, based on StackOverflow posts, in this data set.
Furthermore, we find compelling evidence that out optimizations are effective, for example using probabilistic types removes 1023 false positives errors reports to reduce the total error reports to 324.
The rule graph analysis drastically improves the ranking of importance of the error reports, which allows users to more quickly fix the most critical misconfigurations.
Additionally, \app scales linearly, whereas a previous tool~\cite{santolucitoCAV} showed exponential slow downs on the same benchmark set.

In summary, we make the following contributions.

@@

\markk{maybe we can use these lines in the intro somewhere.}
These errors can cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.
Since these runtime errors may only be triggered after some time in a deployment environment, the standard delta-debugging technique~\cite{x} of starting a system multiple times with different configuration settings will not help detect these misconfigurations.

Our main contributions are as follows:

@@

\item We implement a \app prototype and evaluate it by
conducting comprehensive experiments on real-world dataset.

>>>>

The errors found can cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.
Since these runtime errors may only be triggered after some time in a deployment environment, the standard debugging 
techniques~\cite{Zeller:2005:WPF:1077048} of starting a system multiple times with different configuration settings will not help detect these misconfigurations.

@@

Our learning algorithm surmounts all of difficulties present in 
existing tools.  \app implements a learning
algorithm inspired by {\em association rule
learning}~\cite{agrawal1993mining}. It analyzes a large training set of configuration  files~\cite{configdataset}. Those are real-world reported misconfigurations. A file in the training set might 
contain several different errors and these errors only appear 
in a small percentage of files. We first translate those file into an 
intermediary typed language. With with every type we associate 
a set of very general interfaces. An \app's user does not
need to provide them, they are internally associated to the types. The 
learner then instantiates those interfaces with the keywords appearing in 
the training set. However, since files might also contain errors we take 
this into account when learning correct rules. All learned rules are 
annotated with the probability of correctness.  
To ensure the learned rules are good enough,
\app employs a further analysis to refine the learned rules.
In general, \app builds a graph modeling the learned rules,
and then analyzes this graph to rank the importance
and relevance of the learned rules.

We have implemented a tool, \app, and evaluated it on almost 1000 real-
world configuration files from Github.
We demonstrate that we are able to detect known errors, based on 
StackOverflow posts, in this data set.
Furthermore, we find compelling evidence that out optimizations are 
effective, for example using probabilistic types removes 1023 false 
positives errors reports to reduce the total error reports to 324.
The rule graph analysis drastically improves the ranking of importance of 
the error reports, which allows users to more quickly fix the most 
critical misconfigurations.
Additionally, \app scales linearly, whereas 
a previous tool~\cite{santolucitoCAV} showed exponential slow downs on 
the same benchmark set.

In summary, we make the following contributions:
\begin{itemize}
\item We propose the automated configuration verification
framework, \app, that can learn a language model from a sample
dataset, and then use this language model to verify 
configuration files of interest.
\item We describing the logical foundation of using association rule learning to build a probabilistic specification for configuration files. 
\item We analyze the learned model to further refine the generated specification and we empirically show the usefulness of this approach.
\item We implement a \app prototype and evaluate it by
conducting comprehensive experiments on real-world dataset.

\end{itemize}

@@

@@
